---
title: "meta_data"
output:
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ape)
library(knitr)
mat <- read.csv("raw_data_anuran_call_parameters.csv")
```

# Files 

1. raw_data_anuran_call_parameters.csv
2. amph_2014.tre


## 1. raw_data_anuran_call_parameters.csv

> __Description:__ Dataset with information on anuran advertisement call for 15 species of monkey tree frogs (Anura: Phyllomedusidae).  

__Variables:__  

* ID_can: Unique call indentifier.
* ID_ind: Unique individual identifier.
* ID_pop: Unique population identifier.
* ID_sp: Unique species identifier.
* can: Call number.
* ind: Individual number.
* pop: Population abbreviated name.
* sp: Species name.
* df: Dominant Frequency.
* ci: Call interval.
* pn: Number of pulses.
* pr: Pulse rate.
* pl: Pulse duration.
* BS: Individual Body size.
* TE: Individual temperature.
* LAT: Latitude of the individual.
* LONG: Longitude of the individual.

## 2. amph_2014.tre

> __Description:__ Phylogenetic tree with 2871 Amphibia species ^[Pyron, R.A., and Wiens, J.J. 2011. A large-scale phylogeny of Amphibia including over 2800 species, and a revised classification of extant frogs, salamanders, and caecilians. Mol. Phylogenet. Evol. 61(2): 543–583. Elsevier Inc. doi:10.1016/j.ympev.2011.06.012.].  

```{r include = FALSE}
t <- read.tree(file = "amph_2014.tre")
plot(t, show.tip.label = FALSE, type = "f")
```

